Auditory Scene Similarity Retrieval and Classification with Relevance-based Quantization of Scattering Features

### 2017-06-04 paper/structureScene.tex
minor change to ref to Table DCASE 2016
update keywords

% Note that keywords are not normally used for peerreview paper.
\begin{IEEEkeywords}
acoustic scene classification, acoustic scene similarity retrieval, cluster models, wavelets, scattering, invariance.
\end{IEEEkeywords}

@@

In order to evaluate the generality of our findings, we have taken part in the acoustic scene classification task of the 2016 edition of the DCASE challenge, which was evaluated on a much larger dataset compared to DCASE 2013. For this reason, training support vector machines with the Gaussian RBF kernel proved computationally too demanding and we instead used a linear kernel. Results on DCASE 2013 (see Table \ref{table:dcase2013}) suggests that this provides comparable, albeit slightly worse results. The results on DCASE 2016 (see Table \ref{table:dcase2016}).

>>>>

% Note that keywords are not normally used for peerreview paper.
\begin{IEEEkeywords}
acoustic scene classification, acoustic scene similarity retrieval, scattering transform, clustering, similarity measures.
\end{IEEEkeywords}

@@

In order to evaluate the generality of our findings, we have taken part in the acoustic scene classification task of the 2016 edition of the DCASE challenge, which was evaluated on a much larger dataset compared to DCASE 2013. For this reason, training support vector machines with the Gaussian RBF kernel proved computationally too demanding and we instead used a linear kernel. Results on DCASE 2013 (see Table \ref{table:dcase2013}) suggests that this provides comparable, albeit slightly worse results. The results on DCASE 2016 are reported on Table \ref{table:dcase2016}.
